\section{Common Issues with Modern Billing Automation Products}\label{sec:common-issues-with-modern-billing-automation-products}
When comparing the approaches of the previously presented billing automation solutions, one might notice a common pattern.
All those billing automation solutions employ a three-step-procedure:
\begin{enumerate}
    \item The first step is to scrape multiple information sources to collect as much billing-relevant data as possible.
    \item Next, the systems transform and map the collected unstructured information to their own structured data schema.
    \item Given this now structured dataset, the systems then apply their own techniques to generate billing codes from the data in the schema.
    Those techniques are often AI or rule-based approaches or a hybrid of both.
\end{enumerate}

One of the crucial issues that make automatic billing generation such a difficult task is the following:
Automatic billing generation strictly requires structured and complete data. \addcite
This data often lives as unstructured information scattered across multiple sources such as existing clinical systems or human-readable documents.
Medical records often lack accuracy and completeness of documentation, which strongly correlates with accurate coding \cite{Farhan2005Documentation}.
Additionally, these information sources suffer from differences in quality and redundancies \cite{Scheurwegs2017Selecting}.
The systems presented in section \ref{sec:existing-billing-automation-solutions} rely on these information sources suffering from those issues.
All of them do their best to optimize the data collection step and to reduce the information loss to a minimum.

A solution for that issue could be a billing automation system directly integrated into a clinic information system that guarantees access to all billing-relevant information.
It is crucial that the clinic information system collects the full extent of the billing-relevant information as structured data, making fuzzy data scraping from external sources unnecessary.

