\section{Experimental Rule base}
In this section we introduce the rule base used for the experimental scenarios in this work.

This section serves the following purpose.
Firstly, this section illustrates real examples of

\begin{itemize}
    \item We firstly introduce real that
    \item We illustrate the usage of language features
\end{itemize}

\subsection{GOÄ}
\subsubsection{Base GOÄ rules}

\subsubsubsection{GOÄ 8}
The following rule defines \goa{8}, which is defined as an \mete{Examination to determine the whole body status, including documentation if necessary}.



\lstinputlisting[
language=json,
style=json,
caption={GOÄ 6}
label={lst:goae-8-rule}
]{code/rules/experiments/goae-base-rules-8.json}


\goa{8} is formally defined as an examination of the following organ systems:
\begin{itemize}
    \item the Skin
    \item visible mocous membranes
    \item abdominal organs
    \item supporting and musculoskeletal system organs
    \item orienting neurological examination
\end{itemize}

Note that we use the \code{requiredPhysicalBlocks} field to express conditions on physical examination blocks.
The rule represents each of the mentioned organ systems as a child node of the root node.
The root node applies an \code{AND} operation to all its sub-children.
Each sub-child represents one of the organ systems required by \goa{8}.
The \AVS does not directly define an organ systems examination
However, we can flexibly define an organ system examination by a logical tree of required physical blocks.
This rule defines a skin examination to be present if a \code{skinTurgor}, a \code{skinColor}, a \code{skinThickness} or a \code{skinChangeExamination} block is present.
We can represent the rest of the organ systems in a similar way using the logical tree pattern.
Additionally there is already a respective single block for the orienting neurological examination.

Note that the rule just checks only for existence of examination blocks and does not impose any field conditions.
Unlike \goa{6}, \goa{8} does not mention any additional examination details.
%\goa{6} is very similar to \goa{8} but much larger as it

\subsubsection{GOÄ Surcharges}

The GOÄ defines surcharges that are easily missed out in praxis.
Section \ref{sec:surcharges} introduces this type of GOÄ codes and mentions a few examples.
The following rules are time related and cover inconveniences linked to service provision times.

\lstinputlisting[
language=json,
style=json,
caption={\goa{A: Surcharge for services provided outside of office hours}}
label={lst:goae-A-rule}
]{code/rules/experiments/goae-base-rules-A.json}

\lstinputlisting[
language=json,
style=json,
caption={\goa{B: Surcharge for services provided outside of office hours between 8 p.m. and 10 p.m. or 6 a.m. and 8 a.m}}
label={lst:goae-8-rule}
]{code/rules/experiments/goae-base-rules-B.json}

\lstinputlisting[
language=json,
style=json,
caption={\goa{C: Surcharge for services provided between 10 p.m. and 6 a.m}}
label={lst:goae-C-rule}
]{code/rules/experiments/goae-base-rules-C.json}

\lstinputlisting[
language=json,
style=json,
caption={\goa{D: Surcharge for services provided on Saturdays, Sundays or public holidays}}
label={lst:goae-D-rule}
]{code/rules/experiments/goae-base-rules-D.json}

The following surcharges are applicable to patients younger than 4 years old if one of the required GOÄ codes are present.

\lstinputlisting[
language=json,
style=json,
caption={\goa{K1: Surcharge to the benefits according to numbers 45, 46, 48, 50, 51, 55 or 56 for children up to the age of 4}}
label={lst:goae-K1-rule}
]{code/rules/experiments/goae-base-rules-K1.json}

\lstinputlisting[
language=json,
style=json,
caption={\goa{K2: Surcharge for examinations according to numbers 5, 6, 7 or 8 for children up to the age of 4}}
label={lst:goae-K2-rule}
]{code/rules/experiments/goae-base-rules-K2.json}


\subsubsection{Multiplier Justification Rules}\label{subsec:multiplier-justification-rules}
Section \ref{sec:billing-multipliers} and \ref{sec:multiplier-justifications} introduce the concept of billing multipliers in private treatments.
Multipliers are applicable to existing GOÄ codes, however, require justifying and provable condition in the treatment data.
As multiplier justifications are neither standardized nor pre-defined by any authority,
part of this work was to collect commonly used multiplier justifications.
Thanks to the medical experts at \AV, I received access to medical documents that contained real multiplier justifications used in the Dermato Oncology department of the LMU.
Many of the following rules implement those justifications.
Additionally, I took part in \todo{Explain PVC semianr}


\subsubsubsection{Procedure-specific and duration-related multiplier justifications}
Procedures often take longer than expected.
This can be the case due to unforeseen complications and issues that appear during the procedure.

The following rule list shows the generic pattern used for procedure-specific and duration-related multiplier justifications.

\lstinputlisting[
language=json,
style=json,
caption={\goa{generic procedure duration multiplier justification rule}}
label={lst:goae-K2-rule}
]{code/rules/experiments/goae-base-rules-K2.json}

Note that the rule only checks for the existence of the respective procedure block.
We use the special block condition \code{\$minDuration} to impose a condition on the duration of the provided procedure.
\code{f\(N\)} inside the multiplier object is a linear and increasing function.
The constant makes sure that the image of the function has the upper bound \code{C}, which should be the highest allowed multiplier value for \goa{<code>}.


%As described in section \ref{sec:billing-multipliers} they are merely descriptive comments attached to GOÄ billing positions.


Next, I
