\subsection{The Multiplier Function}\label{subsec:the-multiplier-function}
The multiplier justification rule type does not use the concept of a quantity.
They require \code{condition} blocks to make them derivable for certain conditions.
Additionally, we also want to compute suggested multiplier values dynamically from the environment.
This is why I introduced the \code{multiplier} field, which is very similar to the previously introduced \code{quantity} field.
Both make use of numeric function expressions that allow for dynamic computation from their environment.

In contrast to quantity functions, a multiplier expression returns a positive floating point number with two decimal places.

In this subsection, we illustrate this concept using the following example.
From Dr. Sahra Bojko I have learned that regular laryngoscopies should take at most 20 minutes.
We can apply a duration related multiplier for laryngoscopies that exceed this duration.
The longer the laryngoscopy takes, the greater should be the value of the multiplier for the provided service.
One way of implementing this is by declaring multiple multiplier justification rules applying to different time intervals.

\clearpage
\lstinputlisting[
    language=json,
    style=json,
    caption={Step multiplier function},
    label={lst:multiplier-justification-function-steps}
]{code/rules/specification/multiplier-expression-steps.json}

All three rules logically exclude themselves due to the duration intervals in their \code{laryngoscopy} block conditions.

This implements the following step function declared in equation \ref{eq:multilier-justification-step-function} and illustrated in figure \ref{plot:multiplier-justification-step-function}.

\begin{equation}\label{eq:multilier-justification-step-function}
    f(x) =
    \begin{cases}
        1.5 & \text{for } 20 \leq x < 30, \\
        2.5 & \text{for } 30 \leq x < 40, \\
        3.5 & \text{for } x \geq 40.
    \end{cases}
\end{equation}

\begin{center}
    \label{plot:multiplier-justification-step-function}
    \begin{tikzpicture}
        \begin{axis}
        [
            axis lines=middle,
            xlabel={duration in minutes},
            ylabel={suggested multiplier value},
            xmin=0, xmax=70,
            ymin=0, ymax=4,
            xtick={10,20,30,40,50,60},
            ytick={0,1,2,3,3.5},
            clip=false,
            domain=20:75,
            samples=100,
        ]
            \addplot+[no marks, blue, thick, const plot] coordinates {(20,1.5) (30,2.5) (40,3.5) (70,3.5)};
        \end{axis}
    \end{tikzpicture}
\end{center}

Another more compact way to implement this is using a single rule with a more sophisticated multiplier expression.
Formula \ref{eq:bounded-linear-multiplier-function} is a valid choice for a multiplier function.

\begin{equation}
    \label{eq:bounded-linear-multiplier-function}
    f: \left[20, \infty\right) \rightarrow \left[ 1, \infty \right) : d \mapsto \min\left( 3.5, \frac{5}{40} d - \frac{3}{2} \right)
\end{equation}


Code snippet \ref{lst:multiplier-justification-function-linear} illustrates a rule that implements this multiplier function.
Note that the \code{condition} assures that the rule only applies to treatments with a provided laryngoscopy that took at least \code{20} minutes.
This sets the domain of the function to $\left[20, \infty\right)$.
This way inside, we can inside the \code{multiplier} block safely assume that the duration is greater or equal to 20.

\lstinputlisting[
    language=json,
    style=json,
    caption={Bounded linear multiplier function},
    label={lst:multiplier-justification-function-linear}
]{code/rules/specification/multiplier-expression-linear.json}


\begin{center}
    \begin{tikzpicture}
        \begin{axis}
        [
            axis lines=middle,
            xlabel={duration in minutes},
            ylabel={suggested multiplier value},
            xmin=0, xmax=70,
            ymin=0, ymax=4,
            xtick={0,10,20,30,40,50,60,70},
            ytick={0,1,2,3,3.5,4},
            clip=false,
            domain=20:75,
            samples=100,
        ]
            \addplot+[no marks, blue, thick] {min(5/40*x - 1.5, 3.5)};
        \end{axis}
        \label{plot:linear-mul-just}
    \end{tikzpicture}
\end{center}

Plot \ref{plot:linear-mul-just} illustrates the graph for the multiplier function.

For ordinary laryngoscopies that take less than 20 minutes, the multiplier justification rule does not match at all.
Note that with increasing laryngoscopy duration, the suggested multiplier linearly increases between 20 and 40 minutes.
For very unlikely cases where complications are so severe that the laryngoscopy takes more than 40 minutes, the rule suggests the maximum multiplier value of 3.5.

