\chapter{\abstractname}

This master's thesis presents the development and implementation of a novel rule-based billing framework, designed to be compatible with both statutory and private medical treatments.
The core of this system is a JSON-based domain-specific rule language, tailored for billing experts to encode their domain knowledge effectively.
This language accommodates multiple rule types, including GOÄ, EBM, multiplier justifications, OPS rules, and flatrate rules, demonstrating its universal applicability.
The billing framework is seamlessly integrated into a Java Spring Boot microservice, developed from scratch.
This microservice leverages the encoded rules to generate valid and optimized billing codes from medical treatments.
A significant aspect of this project involved collaboration with Avelios Medical, a company specializing in developing a clinic information system focused on structured data collection.
This collaboration underscores the thesis's key proposition: that automated billing is contingent on the availability of structured data, which Avelios Medical's software provides.
To design the rule language, extensive research was conducted, including interviews with billing experts and participation in a medical seminar focused on private billing.
This research was instrumental in identifying 17 distinct information sources and supporting 41 condition types within the rule language.
The framework's effectiveness was validated through a series of benchmark tests using example treatments provided by billing experts at Avelios Medical.
The framework demonstrated proficiency in deriving most billing codes accurately for complex treatment scenarios.
However, the research also uncovered limitations within the framework, primarily due to certain information not being tracked by Avelios Medical's software.
These gaps, often outside the scope of standard medical documentation or challenging to track automatically, such as consultation durations, highlight areas for future enhancement.
Overall, this thesis contributes significantly to the field of medical billing by introducing a flexible, data-driven solution that streamlines the billing process, ensuring accuracy and efficiency in a complex domain
